### 2014-08-20 Docs/flowchart/flowchart.tex

The compressible momentum equation (written in terms of velocity is):
\begin{equation}
\rho \frac{\partial \Ub}{\partial t} + \rho \Ub \cdot \nabla \Ub + \nabla p = -\rho |g| \er
\end{equation}
Subtracting off the base state, and defining the perturbational
pressure (sometimes called the dynamic pressure) as $\pi \equiv p - p_0$,
and perturbational density as $\rho' \equiv \rho - \rho_0$, we have:
\begin{equation}
\rho \frac{\partial \Ub}{\partial t} + \rho \Ub \cdot \nabla \Ub + \nabla \pi = -\rho' |g| \er
\end{equation}
or
\begin{equation}
\frac{\partial \Ub}{\partial t} + \Ub \cdot \nabla \Ub + \frac{1}{\rho} \nabla \pi =
   -\frac{\rho^\prime}{\rho} |g| \er
\end{equation}
This is the form of the momentum equation that we solved in papers
I--IV and in the multilevel paper.

@@

We decompose the full velocity field into a base state velocity,
$w_0$, that governs the base state dynamics, and a local velocity,
$\Ubt$, that governs the local dynamics, i.e., 
\begin{equation}
\Ub = w_0(r,t)\eb_r + \Ubt(\xb,t).
\end{equation}
with
$\overline{(\Ubt\cdot\eb_r)} = 0$ and
$w_0 = \overline{(\Ub\cdot\eb_r)}$---the motivation for this splitting was given in paper~II.
The velocity evolution equations are then 
\begin{align}
\frac{\partial w_0}{\partial t} &= -w_0\frac{\partial w_0}{\partial
  r} - \frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r},\label{eq:w0
  evolution}\\ 
%
\frac{\partial\Ubt}{\partial t} &= -(\Ubt + w_0\er)\cdot\nabla\Ubt
  - \left(\Ubt\cdot\eb_r\right)\frac{\partial w_0}{\partial r}\eb_r -
\frac{\beta_0}{\rho}\nabla\left(\frac{\pi}{\beta_0} \right) +
\frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r}\eb_r -
\frac{\rho-\rho_0}{\rho}g\eb_r.\label{eq:flow:utildeupd}
\end{align}
where $\pi_0$ is the base state component of the perturbational pressure.
By laterally averaging to equation (\ref{eq:U divergence}),
we obtain a divergence constraint for $w_0$:
\begin{equation}
\nabla\cdot(\beta_0 w_0 \eb_r) = 
    \beta_0\left(\Sbar - \frac{1}{\gammabar p_0}
           \frac{\partial p_0}{\partial t}\right).\label{eq:w0 divergence}
\end{equation}
The divergence constraint for $\Ubt$ can be found by subtracting
(\ref{eq:w0 divergence}) into (\ref{eq:U divergence}), resulting in
\begin{equation}
\nabla\cdot\left(\beta_0\Ubt\right) = \beta_0\left(S-\Sbar\right).\label{eq:utilde divergence}
\end{equation}

>>>>

The compressible momentum equation (written in terms of velocity is):
\begin{equation}
\rho \frac{\partial \Ub}{\partial t} + \rho \Ub \cdot \nabla \Ub + \nabla p = -\rho |g| \er
\end{equation}
Subtracting off the base state, and defining the perturbational
pressure (sometimes called the dynamic pressure) as $\pi = p - p_0$,
and perturbational density as $\rho' = \rho - \rho_0$, we have:
\begin{equation}
\rho \frac{\partial \Ub}{\partial t} + \rho \Ub \cdot \nabla \Ub + \nabla \pi = -\rho' |g| \er
\end{equation}
or
\begin{equation}
\frac{\partial \Ub}{\partial t} + \Ub \cdot \nabla \Ub + \frac{1}{\rho} \nabla \pi =
   -\frac{\rho^\prime}{\rho} |g| \er
\end{equation}
This is the form of the momentum equation that we solved in papers
I--IV and in the multilevel paper.

@@

We decompose the full velocity field into a base state velocity,
$w_0$, that governs the base state dynamics, and a local velocity,
$\Ubt$, that governs the local dynamics, i.e., 
\begin{equation}
\Ub = w_0(r,t)\eb_r + \Ubt(\xb,t).
\end{equation}
with
$\overline{(\Ubt\cdot\eb_r)} = 0$ and
$w_0 = \overline{(\Ub\cdot\eb_r)}$---the motivation for this splitting was given in paper~II.
The velocity evolution equations are then 
\begin{eqnarray}
\frac{\partial w_0}{\partial t} &=& -w_0\frac{\partial w_0}{\partial
  r} - \frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r},\label{eq:w0
  evolution}\\ 
%
\frac{\partial\Ubt}{\partial t} &=& -(\Ubt + w_0\er)\cdot\nabla\Ubt
  - \left(\Ubt\cdot\eb_r\right)\frac{\partial w_0}{\partial r}\eb_r -
\frac{\beta_0}{\rho}\nabla\left(\frac{\pi}{\beta_0} \right) +
\frac{\beta_0}{\rho_0}\frac{\partial(\pi_0/\beta_0)}{\partial r}\eb_r -
\frac{\rho-\rho_0}{\rho}g\eb_r.\label{eq:flow:utildeupd}
\end{eqnarray}
where $\pi_0$ is the base state component of the perturbational pressure.
By laterally averaging to equation (\ref{eq:U divergence}),
we obtain a divergence constraint for $w_0$:
\begin{equation}
\nabla\cdot(\beta_0 w_0 \eb_r) = 
    \beta_0\left(\Sbar - \frac{1}{\gammabar p_0}
           \frac{\partial p_0}{\partial t}\right).\label{eq:w0 divergence}
\end{equation}
The divergence constraint for $\Ubt$ can be found by subtracting
(\ref{eq:w0 divergence}) into (\ref{eq:U divergence}), resulting in
\begin{equation}
\nabla\cdot\left(\beta_0\Ubt\right) = \beta_0\left(S-\Sbar\right).\label{eq:utilde divergence}
\end{equation}

### 2014-08-20 Docs/runtime_parameters/runtime_parameters.tex

\rowcolor{tableShade}
\verb=  small_dens  = &    &  1.d-5 \\
\verb=  small_temp  = &    &  5.d6 \\
\rowcolor{tableShade}
\verb=  use_eos_e_instead_of_h  = &   In deriving the temperature from the $h$, first subtract off $p_0/\rho$ to define $e$, and use that as the input to the EOS.  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  sdc_couple_mac_velocity  = &   recompute MAC velocity at the beginning of each SDC iter if .false., only recompute MAC velocity at the beginning of the first iter  &  .false. \\
\verb=  sdc_hold_mac_velocity  = &   if true, never recompute MAC velocity, no matter what the other sdc flags are  &  .false. \\
\rowcolor{tableShade}
\verb=  sdc_iters  = &   how many SDC iteractions to take (requires the code be compiled with {\tt SDC := t}  &  1 \\

@@

\rowcolor{tableShade}
\verb=  burner_threshold_cutoff  = &   Mass fraction cutoff for burner\_threshold\_species  used in burner threshold  &  1.d-10 \\
\verb=  burner_threshold_species  = &   Name of the species to be used in burner threshold  &  "" \\
\rowcolor{tableShade}
\verb=  do_burning  = &   turn on (.true.) or off (.false.) burning  &  .true. \\

@@

\verb=  use_alt_energy_fix  = &   modify the momentum equation to have $(\beta_0/\rho) \nabla (\pi/\beta_0)$ instead of just $(1/\rho) \nabla (\pi)$  &  .false. \\

@@

\verb=  use_tfromp  = &   When updating temperature, use $T=T(\rho,p_0,X) $ rather than $T=T(\rho,h,X)$.  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  cg_verbose  = &   Verbosity of bottom solver  &  0 \\
\verb=  hg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\rowcolor{tableShade}
\verb=  hg_cycle_type  = &   Type of cycle used in the nodal multigrid -- 1 = F-cycle, 2 = W-cycle, 3 = V-cycle  &  3 \\
\verb=  hg_dense_stencil  = &   In hgproject, in 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).  In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.).  &  .true. \\
\rowcolor{tableShade}
\verb=  max_mg_bottom_nlevels  = &   if mg\_bottom\_solver == 4, then how many mg levels can the bottom solver mgt object have  &  1000 \\
\verb=  mg_bottom_nu  = &   number of smoothing iterations to do after the multigrid bottom solver  &  10 \\
\rowcolor{tableShade}
\verb=  mg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\verb=  mg_cycle_type  = &   Type of cycle used in the MAC multigrid -- 1 = F-cycle, 2 = W-cycle, 3 = V-cycle  &  3 \\
\rowcolor{tableShade}
\verb=  mg_nu_1  = &   number of smoothing iterations to do going down the V-cycle  &  2 \\
\verb=  mg_nu_2  = &   number of smoothing iterations to do going up the V-cycle  &  2 \\
\rowcolor{tableShade}
\verb=  mg_verbose  = &   Verbsoity of the multigrid solver, but not the bottom solver.  &  0 \\
\verb=  use_hypre  = &   use the hypre library  &  .false. \\

>>>>

\rowcolor{tableShade}
\verb=  small_dens  = &    &  1.d-5 \\
\verb=  small_temp  = &    &  5.d6 \\
\rowcolor{tableShade}
\verb=  use_eos_e_instead_of_h  = &   In deriving the temperature from the $h$, first subtract off $p_0/\rho$ to define $e$, and use that as the input to the EOS.  &  .false. \\
\verb=  use_pprime_in_tfromp  = &    &  .false. \\
\rowcolor{tableShade}
\verb=  use_tfromp  = &   When updating temperature, use $T=T(\rho,p_0,X) $ rather than $T=T(\rho,h,X)$.  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  sdc_couple_mac_velocity  = &   recompute MAC velocity at the beginning of each SDC iter  &  .false. \\
\verb=  sdc_iters  = &   how many SDC iteractions to take (requires the code be compiled with {\tt SDC := t}  &  1 \\

@@

\rowcolor{tableShade}
\verb=  burner_threshold_cutoff  = &   Mass fraction cutoff for burner\_threshold\_species  used in burner threshold  &  1.d-10 \\
\verb=  burner_threshold_species  = &   Name of the species to be used in burner threshold  &  "" \\
\rowcolor{tableShade}
\verb=  do_burning  = &   turn on (.true.) or off (.false.) burning  &  .true. \\
\verb=  do_subgrid_burning  = &   break a zone into subzones, call the burner in each subzone and then average the result to the original cell  &  .false. \\

@@

\verb=  use_alt_energy_fix  = &   modify the momentum equation to have $(\beta_0/\rho) \nabla (\pi/\beta_0)$ instead of just $(1/\rho) \nabla (\pi)$  &  .true. \\

@@

@@

\rowcolor{tableShade}
\verb=  cg_verbose  = &   Verbosity of bottom solver  &  0 \\
\verb=  hg_bottom_solver  = &   valid values are $\ge$ 0  &  -1 \\
\rowcolor{tableShade}
\verb=  hg_cycle_type  = &   Type of cycle used in the nodal multigrid -- 1 = F-cycle, 2 = W-cycle, 3 = V-cycle  &  3 \\
\verb=  hg_dense_stencil  = &   In hgproject, in 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).  In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.).  &  .true. \\
\rowcolor{tableShade}
\verb=  max_mg_bottom_nlevels  = &   if mg\_bottom\_solver == 4, then how many mg levels can the bottom solver mgt object have  &  1000 \\
\verb=  mg_bottom_nu  = &   number of smoothing iterations to do after the multigrid bottom solver  &  10 \\
\rowcolor{tableShade}
\verb=  mg_bottom_solver  = &   valid values are $\ge$ 0  &  -1 \\
\verb=  mg_cycle_type  = &   Type of cycle used in the MAC multigrid -- 1 = F-cycle, 2 = W-cycle, 3 = V-cycle  &  3 \\
\rowcolor{tableShade}
\verb=  mg_nu_1  = &   number of smoothing iterations to do going down the V-cycle  &  2 \\
\verb=  mg_nu_2  = &   number of smoothing iterations to do going up the V-cycle  &  2 \\
\rowcolor{tableShade}
\verb=  mg_verbose  = &   Verbsoity of the multigrid solver, but not the bottom solver.  &  0 \\
\verb=  use_hypre  = &   use the hypre library  &  .false. \\
